\textbf{NBA Party}

### 2017-07-14 cardinal_analytx_presentation/nightlife_and_sports.tex
Added commentary to conclusion slide.

\begin{frame}   \frametitle{Future research (MLB and general)}
  \begin{itemize}     
  \item Within the MLB, we can look at statistics such as batting averages or general fielding statistics. 
    \item Possibly prolonged effects; recall our magic 24 hour number.
    \item NHL or European soccer leagues.   \end{itemize} \end{frame}

\begin{frame}   \frametitle{Conclusions}
  \begin{itemize}     \item NBA and MLB players under-perform bookmakers expectations after visiting LA and NY.
    \item In general we see that performance decreases as a function of (our proxy for) nightlife.     \item The decrease in likelihood can (in part) be explained by a drop in defensive performance in the NBA.
    \item With a causal model established, we realize a profitable betting scheme in MLB.   \end{itemize} \end{frame}

>>>>

\begin{frame}   \frametitle{Future research (MLB and general)}
  \begin{itemize}     
    \item Within the MLB, we can look at statistics such as batting averages or general fielding statistics. 
    \vspace{12pt}
    \item Possibly prolonged effects: recall our magic 24 hour number.
      How does the hangover effect taper off as a function of time?
    \vspace{12pt}
    \item NHL or European soccer leagues.   
  \end{itemize} 
\end{frame}

\begin{frame}   \frametitle{Conclusions}
  \begin{itemize}
    \vspace{12pt}
    \item NBA and MLB players under-perform bookmakers expectations after visiting LA and NY.
    \vspace{12pt}
    \item In general we see that performance decreases as a function of (our proxy for) nightlife.     
    \vspace{12pt}
      \item The decrease in likelihood can (in part) be explained by a drop in defensive performance in the NBA.
    \vspace{12pt}
    \item With a causal model established, we realize a profitable betting scheme in MLB.   
  \end{itemize} 
\end{frame}
